All Gene Supplementary Material - Additional samples removed.

### 2017-12-23 all_gene_analysis/all_gene_analysis_additional_treatment_removed.Rmd
updated changes to new supp file

indices <- ids2indices(go.gene.sets, rownames(v2), remove.empty=TRUE)
go_mr <- mroast(v2, index=indices, design=modRUV, contrast=2,
                nrot=10000, set.statistic="floormean")
go_cam <- camera(v2, index=indices, design=modRUV, contrast=2)
kable(go_mr, digits=3)
```

@@

```{r}
kable(go_cam, digits=3)
```

Now KEGG pathway enrichment again making use of mroast and camera.
```{r}
indices <- ids2indices(kegg.gene.sets, rownames(v2))
keg_mr <- mroast(v2, index=indices, design=modRUV, contrast=2, nrot=10000,
                 set.statistic="floormean")
keg_cam <- camera(v2, index=indices, design=modRUV, contrast=2)
kable(keg_mr, digits=3)
```

@@

```{r}
kable(keg_cam, digits=3)
```

>>>>

indices <- ids2indices(go.gene.sets, rownames(v2), remove.empty=TRUE)
go_mr <- mroast(v2, index=indices, design=modRUV, contrast=2,
                nrot=10000, set.statistic="floormean")
go_cam <- camera(v2, index=indices, design=modRUV, contrast=2)

go_mr$PValue <- format(go_mr$PValue, scientific=TRUE, digits=3)
go_mr$FDR <- format(go_mr$FDR, scientific=TRUE, digits=3)
go_mr$PValue.Mixed <- format(go_mr$PValue.Mixed, scientific=TRUE, digits=3)
go_mr$FDR.Mixed <- format(go_mr$FDR.Mixed, scientific=TRUE, digits=3)
kable(go_mr, digits=3)
```

@@

```{r}
go_cam$PValue <- format(go_cam$PValue, scientific=TRUE, digits=3)
go_cam$FDR <- format(go_cam$FDR, scientific=TRUE, digits=3)
kable(go_cam)
```

Now KEGG pathway enrichment again making use of mroast and camera.
```{r}
indices <- ids2indices(kegg.gene.sets, rownames(v2))
keg_mr <- mroast(v2, index=indices, design=modRUV, contrast=2, nrot=10000,
                 set.statistic="floormean")
keg_cam <- camera(v2, index=indices, design=modRUV, contrast=2)

keg_mr$PValue <- format(keg_mr$PValue, scientific=TRUE, digits=3)
keg_mr$FDR <- format(keg_mr$FDR, scientific=TRUE, digits=3)
keg_mr$PValue.Mixed <- format(keg_mr$PValue.Mixed, scientific=TRUE, digits=3)
keg_mr$FDR.Mixed <- format(keg_mr$FDR.Mixed, scientific=TRUE, digits=3)
kable(keg_mr, digits=3)
```

@@

```{r}
keg_cam$PValue <- format(keg_cam$PValue, scientific=TRUE, digits=3)
keg_cam$FDR <- format(keg_cam$FDR, scientific=TRUE, digits=3)
kable(keg_cam, digits=3)
```
